Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2013-01-14 chi2013-webbox.tex
Updated epsrc acknowledgement to standard form and added heather's EPSRC acknowledgement

@@

The work presented in this paper was sponsored by the EPSRC project SOCIAM (Ref. EP/J017728/1).  We would like to thank our collaborators Wendy Hall, mc schraefel, Tim Berners-Lee, Kieron O'Hara, Susan Davies, Maraim Elbadri, Tom Smith, Yang Yang, Igor Popov, and Shauna VanKleek whose help and advice have shaped this work throughout.

>>>>

\hyphenation{EPSRC SOCIAM}

@@

The work presented in this paper was supported by the SOCIAM project, funded by the Engineering and Physical Sciences Research Council under contract EP/J017728/1. Dr Packer is grateful for funding from the EPSRC in the form of a Post Doctoral Award.  We would like to thank our collaborators Wendy Hall, mc schraefel, Tim Berners-Lee, Kieron O'Hara, Susan Davies, Maraim Elbadri, Tom Smith, Yang Yang, Igor Popov, and Shauna VanKleek whose help and advice have shaped this work throughout.
